\documentclass[a4paper,11pt]{exam}
    \usepackage{hyperref}
    \ifx\pdftexversion\undefined
       \usepackage{epsfig}
    \else
       \usepackage[pdftex]{graphics}
    \fi
    \usepackage{epsfig}
\begin{document}
    \extraheadheight{.5in}
    \firstpageheader{\large\sf CS2105}%
    {\large\sf National University of Singapore\\ School of Computing \\
    \LARGE\sf Problem Set 1}%
    {\large\sf Semester 2 10/11}
    \firstpageheadrule
    \pagestyle{headandfoot}

    \begin{questions}
	\question \textbf{(KR, Chapter 1, Problem 5)} Consider two hosts, A and B,
	connected by a single link of rate $R$ bps.  Suppose that the two hosts
	are separated by $m$ meters, and suppose the propagation speed along the
	link is $s$ meters/sec.  Host A is to send a packet of size $L$ bits to
	Host B.
    \begin{parts}
	\part Express the propagation delay, $d_{prop}$, in terms of $m$ and $s$.
	\part Determine the transmission time of the packet, $d_{trans}$, in
	terms of $L$ and $R$.
	\part Ignoring processing and queueing delays, obtain an expression for
	the end-to-end delay.
	\part Suppose Host A begins to transmit the packet at time $t$ = 0.  At
	time $t = d_{trans}$, where is the last bit of the packet?
	\part Suppose $d_{prop}$ is greater than $d_{trans}$.  At time $t =
	d_{trans}$, where is the first bit of the packet?
	\part Suppose $d_{prop}$ is less than $d_{trans}$.  At time $t =
	d_{trans}$, where is the first bit of the packet?
	\part Suppose $s = 2.5 \times 10^8$, $L$ = 100 bits, and $R = 28$ kbps.
	Find the distance $m$ so that $d_{prop}$ equals $d_{trans}$.
    \end{parts}

	\question \textbf{(KR, Chapter 1, Problem 6)} 
	Suppose users share a 1
	Mbps link.  Also suppose each user requires 100 kbps when transmitting,
	but each user transmits only 10 percent of the time.  (See Section 1.3,
	KR).  
	\begin{parts}
	\part When circuit switching is used, how many users can be supported?
	\part For the remainder of this problem, suppose packet switching is
	used.  Find the probability that a given user is transmitting.
	\part Suppose there are 40 users.  Find the probability that at any given
	time, exactly $n$ users are transmitting simultaneously.  (Hint: Use the
	binomial distribution).
	\part Find the probability that there are 11 or more users transmitting
	simultaneously.
	\end{parts}

	\question \textbf{(KR, Chapter 1, Problem 23)} 
	Suppose two hosts, A and B, are separated by 100,000 kilometers
	and are connected by a direct link of $R = 1$ Mbps.  Suppose the
	propagation speed over the link is $2.5 \times 10^8$ meters/sec.
	\begin{parts}
	\part Calculate the bandwidth-delay product, $R \times t_{prop}$.
	\part Consider sending a file of 400,000 bits from Host A to Host B.
	Suppose the file is sent continuously as one big message.  What is the
	maximum number of bits that will be in the link at any given time?
	\part Provide an interpretation of the bandwidth-delay product.
	\part What is the width (in meters) of a bit in the link?  Is it longer
	than a soccer field?  (A standard soccer field is between 90 to 120 m long)
    \part Derive a general expression for the width of a bit in terms of the
	propagation speed $s$, the transmission rate $R$, and the length of the
	link $m$.
	\end{parts}

    \pagebreak

	\question \textbf{(KR, Chapter 1, Problem 24)} 
	In modern packet-switched networks, the source host segments
	long, application-layer messages (for example, an image or a music file)
	into smaller packets and sends the packets into the network.  The
	receiver then reassembles the packets back  into the original message.
	We refer to this process as \textit{message segmentation.}  (See 
	Figure 1.28 in KR, page 103).  

	Consider a message that is $7.5\times 10^6$ bits long that is to be sent
	from a source to destination, through two packet switches.  Suppose each 
	link in the figure is 1.5 Mbps.  Ignore propagation, queuing and
	processing delays.

	\begin{parts}
	\part Consider sending the message from source to destination
	\textit{without} message segmentation.  How long does it take to move the
	message from the source host to the first packet switch?  Keeping in mind
	that each switch uses store-and-forward packet switching, what is the
	total time to move the message from source host to destination host?

	\part Now suppose that the message is segmented into 5,000 packets, with
	each packet being 1,500 bits long.  How long does it take to move the
	first packet from source host to the first switch?  When the first packet
	is being sent from the first switch to the second switch, the second
	packet is being sent from the source host to the second switch.  At what
	time will the second packet be fully received at the first switch?

	\part How long does it take to move the file from source host to
	destination host when message segmentation is used?  Compare this result
	with your answer in part (a) and comment.

	\part Discuss the drawbacks of message segmentation.
	\end{parts}

	\question \textbf{(KR, Chapter 1, Problem 25)} 
	Consider sending a large file of $F$ bits from Host A to Host B.  There
	are two links (and one switch) between A and B, and the links are
	uncongested (that is, no queuing delays).  Host A segments the file into
	segments of $S$ bits each and adds 40 bits of headers to each segment,
	forming packets of $L = 40 + S$ bits.  Each link has a transmission rate
	of $R$ bps. Find the value of $S$ that minimizes the delay of moving the
	file from Host A to Host B.  Disregard propagation delay.
    \end{questions}
\end{document}
