\documentclass[a4paper,11pt]{exam}
    \usepackage{hyperref}
    \ifx\pdftexversion\undefined
       \usepackage{epsfig}
    \else
       \usepackage[pdftex]{graphics}
    \fi
    \usepackage{epsfig}
\begin{document}
\extraheadheight{.5in}
\firstpageheader{\large\sf CS2105}%
{\large\sf National University of Singapore\\ School of Computing \\
\LARGE\sf Problem Set 2}%
{\large\sf Semester 2 13/14}
\firstpageheadrule
\pagestyle{headandfoot}

\begin{questions}

\question \textbf{(Modified from KR, Chapter 2, P7)}
Suppose within your Web browser you click on a link to obtain a
Web page.  The IP address for the associated URL is not cached
in your local host, so a DNS lookup is necessary to obtain the
IP address.  

Suppose that $n$ DNS servers are visited before your
host receives the IP address from DNS; visiting them incurs 
an RTT of $D_{DNS}$ per DNS server.

Further suppose that
the Web page associated with the link contains $m$ very small objects. 
Suppose the HTTP running is non-persistent and non-parallel.  Let 
$D_{Web}$
denote the RTT between the local host and the server of each
object.  

Assuming zero transmission time of each object, how
much time elapses from when the client clicks on the link until
the client receives all the objects?

\question \textbf{(Modified from KR, Chapter 2, P8)}
Referring to the previous question, suppose that three DNS servers are visited.  Further, the HTML file
references five very small objects on the same server.

Neglecting transmission time, how much time elapses with:
\begin{parts}
\part Non-persistent HTTP with no parallel TCP connections? 
\part Non-persistent HTTP with the browser configured for five parallel connections? 
\part Persistent HTTP with pipelining?
\end{parts}

\question 
Suppose a malicious party can intercept your HTTP GET requests (but not necessary your HTTP responses) and have access to your cookie.  Explain how this could lead to undesirable circumstances.

\question
Suppose a malicious party can insert fake DNS records into DNS servers.  Suggest three different ways how this can be abused.

\end{questions}
\end{document}
