\documentclass[a4paper,11pt]{exam}
    \usepackage{hyperref}
    \ifx\pdftexversion\undefined
       \usepackage{epsfig}
    \else
       \usepackage[pdftex]{graphics}
    \fi
    \usepackage{epsfig}
\begin{document}
    \extraheadheight{.5in}
    \firstpageheader{\large\sf CS2105}%
    {\large\sf National University of Singapore\\ School of Computing \\
    \LARGE\sf Problem Set 3}%
    {\large\sf Semester 2 10/11}
    \firstpageheadrule
    \pagestyle{headandfoot}

    \begin{questions}
	\question \textbf{(KR, Chapter 3, Problem 7)} 
	Draw the FSM for the receiver side of protocol rdt 3.0.

	\question \textbf{(KR, Chapter 3, Problem 11)} 
	Show that if the network connection between the sender and 
	receiver can reorder messages (that is, that two messages 
	propagating in the medium between the sender and receiver 
	can be reordered), then the alternting-bit protocol rdt 3.0 
	will not work correctly.  

	\question \textbf{(KR, Chapter 3, Problem 13)} 
	Consider a reliable data transfer protocol that uses \textit{only}
	negative acknowledgements.  Suppose the sender sends data only
	infrequently.  Would a NAK-only protocol be preferable to 
	a protocol that uses ACKs?  Why?  
	
	Now suppose the sender has a lot of data to send and the 
	end-to-end connection experiences few losses.  In this
	second case, would a NAK-only protocol be preferable to a 
	protocol that uses ACKs?  Why?

	\question \textbf{(KR, Chapter 3, Problem 14)} 
	Consider the GBN (Go-Back-N) protocol with a sender window size of 3 and a sequence
	number range of 1,024. Suppose that at time $t$, the next in-order packet
	that the receiver is expecting has a sequence number of $k$. Assume that the
	medium does not reorder messages. Answer the following questions:
    \begin{parts}
	\part What are the possible sets of sequence numbers inside the sender's window
	at time $t$? Justify your answer.
	\part What are the possible values of the ACK field in all possible messages
	currently propagating back to the sender at time $t$? Justify your answer.
    \end{parts}

	\question \textbf{(KR, Chapter 3, Problem 20)} 
	Answer true-or-false to the following questions and briefly justify your
	answer.
	\begin{parts}
	\part The alternating-bit protocol is the same as the SR protocol with a sender and receiver window size of 1.
	\part The alternating-bit protocol is the same as the GBN protocol with a sender and receiver window size of 1.
	\part With GBN, it is possible for the sender to receive an ACK for a packet that falls outside of its current window. 
	\part With SR, it is possible for the sender to receive an ACK for a packet that falls outside of its current window. 
	\end{parts}

	\question \textbf{(KR, Chapter 3, Problem 22)} 
	Consider the GBN and SR protocols. Suppose the sequence
	number space is of size $k$. What is the largest allowable sender window that
	will avoid the occurrence of problems such as that in Figure 3.27 for each of
	these protocols?

    \end{questions}
\end{document}
